Test SUSIE for regions near genes (500kb flanking)

### 2020-06-24 analysis/simulation-susie-ukbchr22-gtex.adipose.Rmd
susie more examples

```{r sim 5 examples, include= F, echo = F, eval = F, warning= F}
# displaying not right
resall <- Sys.glob(paste0(outputdir, tag, ".", tag2, "*-susieres.txt"))
l <- htmltools::tagList()
res <- resall[1]
for (i in 1:8){
  res <- resall[i]
  name <- gsub(".*res-(.+)-susie.*", "\\1", res)
  l[[i]] <- plot_all(res, mrashres.gene, mrashres.snp, name)
}
l
```

>>>>

```{r sim 5, include= F, echo = F, eval = F, warning= F}
# displaying not right
resall <- Sys.glob(paste0(outputdir, tag, ".", tag2, "*-susieres.txt"))
l <- htmltools::tagList()
res <- resall[1]
for (i in 1:8){
  res <- resall[i]
  name <- gsub(".*res-(.+)-susie.*", "\\1", res)
  l[[i]] <- plot_all(res, mrashres.gene, mrashres.snp, name)
}
l
```
